Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
fixed notation and domains in 4.3

In order to obtain a sound synthesis of the digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered. Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation is written for the system in Figure~\ref{fig:sampledsystem}, considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller ($\hat{C}(z)$):
\begin{equation}
\hat{Y}(z)=\hat{C}(z)\hat{G}(z)[R(z)+\nu_{1}(z)]+\nu_{2}(z)\hat{G}(z)-\hat{Y}(z)\hat{C}(z)\hat{G}(z),
\end{equation}
that can be rewritten as follows:
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}[R(z)+\nu_{1}(z)]+H_{2}(z)\nu_{2}(z),
\end{equation}
where
\begin{equation}
H_{1}=\frac{\hat{C}(z)\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}
and
\begin{equation}
H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}

A discrete-time linear system is said to be Bounded-Input and Bounded-Output (BIBO) stable if and only if every pole of its transfer function lies inside the unit circle. \textcolor{red}{Analyzing Eq.~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for BIBO stability of closed-loop system in Figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.}

@@

%------------------------------------
\subsection{Synthesis Process using DSVerifier}
\label{verification-flow}
%------------------------------------

@@

The full synthesis process is illustrated in Fig.~\ref{DSVerifier_process};
a detailed description of DSVerifier tool can be found in~\cite{IsmailBCFF15}.
Steps $1$ to $5$ are performed by the user/synthesiser and
Steps A to D are automatically performed by DSVerifier.
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

@@

This intermediate ANSI-C code model $(\tilde C(z),\mathfrak{G}(z),\phi)$
containing a specification $\phi$ for the verification properties ({\it
i.e.}, robust stability) is provided to CBMC's~\cite{ClarkeKL04} integrated
CEGIS synthesis module, where $\tilde C(z)$ is marked as input variable to
synthesise.  If any property violation is found, then
a counterexample is reported, which contains system inputs or
parametric deviations $\Delta{G}$ that lead the system to a failure.  
This information allows the CEGIS module to refine its search for a stable
controller, which we explain in detail in section~\ref{synthesiser-general}.
A successful verification result is reported if the system is safe with
respect to $\phi$.  In particular, the stability verification is complete
and sound, since it does not depend on system inputs and outputs.  In the
case of stability, the specification $\phi$ consists in a number of
assumptions on the polynomial coefficients, following Jury's Criteria, as
well as the restrictions set in the representation of these coefficients by
the function $f$ (cf.~Eq.~\eqref{FWL_tf}).

@@

\subsection{General architecture of the program synthesiser}
\label{synthesiser-general}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesiser is of the
form $\exists \vec{P} . \forall \vec{x}. \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions,
$\vec{x}$ ranges over ground terms and $\sigma$ is a quantifier-free
formula.  We interpret the ground terms over some finite domain
$\mathcal{D}$.

@@

\paragraph{Property specification}
Next, we describe the specific property that we pass to the program
synthesiser as the specification $\sigma$.  There are two different
algorithms in DSVerifier that can be used for stability
verification~\cite{daes20161,Bessa16}, one based on
Schur's decomposition and another one based on Jury's
criteria~\cite{astrom1997computer}.  Here, we choose Jury's
method~\cite{astrom1997computer}, due to its efficiency.

@@

Essentially, the synthesis problem we are trying to solve is the following:
find a digital controller denoted by  $N_c$ and $D_c$ that
makes the closed-loop system stable 
for all possible uncertainties $\Delta{\vec{p}}$ (\ref{eq:uncertainty}).
%$(\Delta N_G, \Delta D_G)$. 
% Note that, similar to the rest of the paper, we use the notation 
% $\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
% $\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
When mapping back to the notation used for describing the general architecture 
of the program synthesiser, the controller $(N_c,D_c)$ denotes $P$ and 
$\Delta{\vec{p}}$ represents $x$.

@@

\paragraph{Use of fixed-point computation in the program synthesis engine}
The program synthesis engine uses fixed-point arithmetic.
Thus, we compute the coefficients for $N_c$ and $D_c$ in the domains 
$\mathbb{R}^{n_C}\param{I}{F}$ and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, where 
$n_C$ and $m_C$ denote the order of the corresponding polynomials
and $I$ and $F$ denote the integer and fractional size, respectively.
Regarding the uncertainty, this is synthesised over the 
domain $\mathbb{R}^{n_G+m_G}\param{I_b}{F_b}$, where $n_G$ and $m_G$ 
denote the order of the polynomials representing the 
numerator and denominator of the plant's transfer function, respectively. 
Again, $I_b$ and $F_b$ denote the integer and fractional size, respectively, with
$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.

@@

>>>>

In order to obtain a sound synthesis of digital controller, the effect of FWL implementation in controller and quantisation noises in closed loop system have to be considered. Considering that the quantizer $Q1$ is the source of a white noise $\nu_{1}$ and $Q2$ is the source of a white noise $\nu_{2}$, the following equation may be written for the system in figure~\ref{fig:sampledsystem} considering the parametric uncertainties $\Delta G(z)$ and the FWL effects on controller  ($\hat{C}(z)$):
\begin{equation}
\hat{Y}(z)=\hat{C}(z)\hat{G}(z)[R(z)+\nu_{1}(z)]+\nu_{2}(z)\hat{G}(z)-\hat{Y}(z)\hat{C}(z)\hat{G}(z),
\end{equation}
that can be rewritten as follows:
\begin{equation}
\label{eq:outputfunctions}
\hat{Y}(z)=H_{1}[R(z)+\nu_{1}(z)]+H_{2}(z)\nu_{2}(z),
\end{equation}
where
\begin{equation}
H_{1}=\frac{\hat{C}(z)\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}
and
\begin{equation}
H_{2}=\frac{\hat{G}(z)}{1+\hat{C}(z)\hat{G}(z)},
\end{equation}

A discrete-time linear system is said to be Bounded-Input and Bounded-Output (BIBO) stable if and only if every pole of its transfer function lies inside the unit circle. Analyzing the~\eqref{eq:outputfunctions} and based on assumption~\ref{assumption:cont_and_plant}, the following lemma states necessary conditions for BIBO stability of closed-loop system in figure~\ref{fig:sampledsystem}, since the the exogenous signals $R(z)$, $\nu_{1}$, and $\nu_{2}$ are bounded.

@@

%------------------------------------
\subsection{DSVerifier Verification Flow}
\label{verification-flow}
%------------------------------------

@@

The DSVerifier verification flow is illustrated in Fig.~\ref{DSVerifier_process};
a detailed description of DSVerifier tool can be found in~\cite{IsmailBCFF15}.
Steps $1$ to $5$ are performed by the user/synthesiser and
Steps A to D are automatically performed by DSVerifier.
%, which accepts the
%digital controller transfer functions together with the plant model.  For
%any digital controller, implementation details should be provided ({\it
%e.g.}, number of bits, realization, and sample time).

@@

This intermediate ANSI-C code model $(\tilde C(z),\mathfrak{G}(z),\phi)$
containing a specification $\phi$ for the verification properties ({\it
i.e.}, robust stability) is translated into SAT/SMT formulae by a back-end
model-checking tool ({\it e.g.}, CBMC~\cite{ClarkeKL04} or
ESBMC~\cite{CordeiroFM12}).  If any property violation is found, then
DSVerifier reports a counterexample, which contains system inputs or
parametric deviations $\Delta{G}$ that lead the system to a failure.  A
successful verification result is reported if the system is safe with
respect to $\phi$.  In particular, the stability verification is complete
and sound, since it does not depend on system inputs and outputs.  In the
case of stability, the specification $\phi$ consists in a number of
assumptions on the polynomial coefficients, following Jury's Criteria, as
well as the restrictions set in the representation of these coefficients by
the function $f$ (cf.~Eq.~\eqref{FWL_tf}).

\textcolor{red}{Pascal: can you please update this section to include the CEGIS step?}

@@

\subsection{General architecture of the program synthesiser}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesiser is of the
form $\exists \vec{P} . \forall \vec{x}. \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions,
$\vec{x}$ ranges over ground terms and $\sigma$ is a quantifier-free
formula.  We interpret the ground terms over some finite domain
$\mathcal{D}$.

@@

\paragraph{Property specification}
Next, we describe the specific property that we pass to the program
synthesiser as the specification $\sigma$.  There are two different
algorithms in DSVerifier that can be used for stability
verification~\cite{DBLP:journals/dafes/BessaICF16}, one based on
Schur's decomposition and another one based on Jury's
criteria~\cite{astrom1997computer}.  Here, we choose Jury's
method~\cite{astrom1997computer}, due to its efficiency.

@@

@@

\paragraph{Use of fixed-point computation in the program synthesis engine}
The program synthesis engine uses fixed-point arithmetic.
Namely, we use the domain $\mathbb{R}\param{I}{F}$
for the controller's coefficients and the domain 
$\mathbb{R}\param{I_b}{F_b}$ for the plant's coefficients.
Note that $I$ and $F$, as well as $I_b$ and $F_b$, 
denote the integer and fractional size, respectively, with
$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
%the coefficients for $C(z)$ 
%$N_c$ and $D_c$ 
%in the domain $\mathbb{R}\param{I}{F}$, 
%and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, 
%where $n_C$ and $m_C$ denote the order of the corresponding polynomials
%where $I$ and $F$ denote the integer and fractional size, respectively.
%Regarding the plant, its coefficients are this is synthesised over the 
%domain $\mathbb{R}^{n_G+m_G}\param{I_b}{F_b}$, where $n_G$ and $m_G$ 
%denote the order of the polynomials representing the 
%numerator and denominator of the plant's transfer function, respectively. 
%Again, $I_b$ and $F_b$ denote the integer and fractional size, respectively, with
%$\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.

@@

\paragraph{Our synthesis problem}
The synthesis problem we are trying to solve is the following:
find a digital controller $C(z)$ %denoted by  $N_c$ and $D_c$ 
that makes the closed-loop system stable 
for all possible uncertainties 
%$\Delta{\vec{p}}$ (\ref{eq:uncertainty}).
$\tilde G(z)$ (\ref{digital_plant_tf}).
%, where we precisely describe 
%$(\Delta N_G, \Delta D_G)$. 
% Note that, similar to the rest of the paper, we use the notation 
% $\tilda{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
% $\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
When mapping back to the notation used for describing the general architecture 
of the program synthesiser, the controller $C(z)$ denotes $P$ and 
$\tilde G(z)$ represents $x$.

As mentioned above, we compute the coefficients for $C(z)$ 
%$N_c$ and $D_c$ 
in the domain $\mathbb{R}\param{I}{F}$, 
%and $\mathbb{R}^{m_C}\param{I}{F}$, respectively, 
%where $n_C$ and $m_C$ denote the order of the corresponding polynomials
and those for $\tilde G(z)$ in the domain
$\mathbb{R}\langle I_b,F_b \rangle$.
